%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size
\usepackage{datenumber,fp}

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------
%	AGE CALCULATION
%       https://tex.stackexchange.com/questions/11436/automated-age-calculation
%----------------------------------------------------------------------------------------

\newcounter{dateone}
\newcounter{datetwo}
\newcounter{myagenotrounded}
\setmydatenumber{dateone}{1980}{06}{22}
\setmydatenumber{datetwo}{\the\year}{\the\month}{\the\day}
\FPsub\result{\thedatetwo}{\thedateone}
\FPdiv\myagenotrounded{\result}{365.2425}
\FPtrunc\myage{\myagenotrounded}{0}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Alexander Godin -- Résumé} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> Orber Straße 16, \\ % Address line 1
\> 14193 Berlin, Germany \\ % Address line 2
{\bf Date of Birth} \> 22$^{nd}$ June 1980 (\myage\ years)\\ % Date of birth 
\end{tabbing}}
\vspace{-10mm}
\hfill
\parbox{0.5\textwidth}{
\begin{tabbing}
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \> +49 15207498137 \\ % Mobile phone
{\bf Email} \> \href{mailto:godin.a.e@gmail.com}{godin.a.e@gmail.com}
\end{tabbing}}
\parbox{0.5\textwidth}{
\begin{tabbing}
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf LinkedIn} \> \href{https://www.linkedin.com/in/alexander-godin-4ba9bb1}{https://www.linkedin.com/in/alexander-godin-4ba9bb1}
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Summary Statement}

Software development team lead and architect with 20+ years experience, specializing 
in high-performance reliable electronic trading systems and computer-aided design.
Focused on delivery, hard-working, flexible with proven analytical skills. Adept in design
and architecture, software development process, building distributed teams, leading by example,
managing customer expectations, organization of support of existing systems. Successful in
driving projects with unstable requirements to production in complex enterprise landscape.
Continue coding and reviewing code as "must have" practice for team lead. \\

I am equally interested in growth in one of two directions:
{\begin{itemize}
\item{In-depth: team lead. Hands-on leadership of small/medium-sized development team in complex business area, 
delivering mission-critical, loaded systems.}
\item{In-breadth: lead of team leads. Be responsible for wider scope, less coding, more reviewing and desigining,
 working with team leads.}
\end{itemize}}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{June 2019 -}{Present}
{Deutsche Bank AG, Berlin}
{http://www.db.com}
{Chief Technology Manager}
{Foreign Exchange (FX) IT department in Berlin, Head of FX Derivatives development team.
I started from FX Options Market Data stack rework, leading group of 10 engineers, and over the time extended my leadership role
to several application stacks, responsible for management of FX Options Volatility Models, Pricing of Products and Risk Management of books.
It is a set of mission-critical applications for several Derivative desks, 24/5.5, fault tolerant, with extra focus on finance models calculation accuracy.
Managing 10+ teams with total headcount of 120 people, across 3 locations. Responsible for Vision, defining Book of Work and delivery timelines
with stakeholders, building target stack architecture, stability and observability. Also focused on people management, hiring and growing the team,
improving team efficiency.}
{\begin{itemize}
\item{Lead development of new platform for managing FX Options volatility models, that provides electronic processing of hierarchical models
for 1000+ pairs with sub-second latency.}
\item{Lead development of new platform for automated generation and distribution of reports to internal and external clients.}
\end{itemize}}
{\rule{0mm}{5mm}\textbf{Technologies:} Core Java 11, 17, Kotlin, Spring Boot, Tibco JMS, Redis, Kafka\\
\rule{0mm}{5mm}\textbf{Operating Systems:} SUSE Linux Enterprise 11, RedHat Enterprise 8 (Server). Google Anthos,
Kubernetes, Windows Server 2019\\
\rule{0mm}{5mm}\textbf{SDLC:} Atlassian Confluence, Jira, BitBucket, IntelliJ Idea/PyCharm, Gradle/Maven, Jenkins/TeamCity,  
ITRS Geneos, Prometheus/Grafana.
}

%------------------------------------------------
\clearpage

\job
{Nov 2011 -}{June 2019}
{Deutsche Bank Technology Center, Moscow}
{http://www.db.com}
{Lead Software Development Engineer / Lead Technology Manager}
{Equities Algo Trading IT department in Moscow, focused on two main areas: development of frameworks for
writing trading strategies (including implementing strategies themselves), and building software 
for pre- and real-time  trading analytics. I started working in area of portfolio risk trading strategies,
with responsibilities to develop math model and software, within time moving to team lead of group of 5 people,
utilizing Scrum/Kanban and finally to technology manager, with 20+ people in my teams,
covering wide products line.}
{\begin{itemize}
\item{Designed and delivered to production automated big (2000+ stocks) portfolio trading engine on C++,
aiming trading in optimal manner, based on trader preference on frontier between risk and cost. 
Promoted to Vice President for that (2013).}
\item{Co-designed and implemented portfolio pre-trade client-server analytical system for equities markets.
Server-side was written on combination of C++ and Python, GUI on C\#.}
\item{Designed, lead development and rollout of automated trading container on Java, with C\# and Web GUI.
4 instances in major financial hubs, 20 production servers globally. System performed hedging of trades,
various types of market making and unwinding big portfolio of stocks and ETFs. Buildout required direct
involvement of quants and trading desks into planning and development to have very fast cycle of delivering
business ideas to production (1-2 releases per week). Responsible for architecture, design, forming
global team of developers, setup of SDLC, releases planning, monitoring, setting up proactive support.
Grew several team leads, forming teams, reporting to me. Promoted to Director for that (2019).}
\end{itemize}}
{\rule{0mm}{5mm}\textbf{Technologies:} Core Java 8/Spring, C++03/STL/Boost, Python2/3, Numpy/Scipy, MySQL, TCP/HTTP/WebSockets,
Informatica LBM/Tibco Rendezvous/Solace, Bash, ASP.NET/C\#/WPF, Oracle SQL, Apache Tomcat.\\
\rule{0mm}{5mm}\textbf{Operating Systems:} SUSE Linux Enterprise 11, RedHat Enterprise 7 (Server), Windows 7 (GUI, IDE).\\
\rule{0mm}{5mm}\textbf{SDLC:} Atlassian Confluence/Jira/BitBucket, IntelliJ Idea/PyCharm, Eclipse CDT/PyDev, GIT/SVN,
Maven, Jenkins/TeamCity, Nose/Cucumber(Python), JUnit, IBM UrbanCode, ITRS Geneos, Valgrind, GProf, GCov/Coverage(Python).
}

%------------------------------------------------

\job
{Apr 2007 -}{Nov 2011}
{Deutsche Bank, Moscow}
{http://www.db.com}
{Senior Software Development Engineer / Team Lead}
{Global Equities Trading IT department in Moscow, developing Execution Management System (EMS) of direct market access,
single stock and portfolio trading. Large development team in Moscow (40+ developers), working closely with regional IT 
and support teams. I started as a server-side developer, focusing on bringing market data to the system, then was realigned
to Asia-specific business logic design and coding. In couple of years I became team lead for Asia stream, 
leading small group of 5 people. Server-side components were written on C++, contained 100+ working threads,
and were interconnected by Tibco messaging bus. Automated tests were written on C++/Perl.}
{\begin{itemize}
\item{Implementation of big amount of core features and business-logic, specific to Asia, often then re-usable in other regions.}
\item{Responsible for analysis of requirements and planning scope of releases with Asia regional teams.}
\item{Successful replacement of old systems in India and Taiwan by our EMS, from planning, estimates to final rollout.
Promoted to Assistant Vice President for that (2010).}
\end{itemize}}
{\rule{0mm}{5mm}\textbf{Technologies:} C++/STL (Sun), PThreads, Tibco Rendezvous, Perl, Core Java 6, Oracle SQL.\\
\rule{0mm}{5mm}\textbf{Operating Systems:} Sun (Oracle) Solaris for x86/x64 (Server), Windows XP (GUI, IDE).\\
\rule{0mm}{5mm}\textbf{SDLC:} Atlassian Jira, Visual Studio, SVN, CMake, Hudson, GDB.
}

%------------------------------------------------
\clearpage

\job
{Mar 2006 -}{Apr 2007}
{Intel, Moscow}
{http://www.intel.com}
{Senior Software Developer}
{Electronic design automation department of Intel, developing in-house tools for designing Intel processors.
I was a member of a team of 5 people, focusing on electrical properties of circuit components, formed from several 
field transistors. My specialization was analysis of elements resistance to "soft errors", i.e. possible
flip of value of field transistor when heavy particle arrives, this was more Research and Development (R\&D) job.
Knowledge field required understanding of physics of transistors and way of simulating "soft errors" programmatically.
We used C++ algorithms to model components and their properties.}
{\begin{itemize}
\item{Prepared and released next generation of the tool, based on modern dependency tools and requirements.}
\item{Contribution (research, presentations) to global "soft errors" working group.}
\end{itemize}}
{\rule{0mm}{5mm}\textbf{Technologies:} C++/STL (gcc), PThreads, TCL.\\
\rule{0mm}{5mm}\textbf{Operating Systems:} SUSE Linux Enterprise Server 9 (Server).\\
\rule{0mm}{5mm}\textbf{SDLC:} VIM, Rational ClearCase, Make, GDB/DDD, Valgrind, GProf, GCov.
}

%------------------------------------------------

\job
{Jul 2002 -}{Mar 2006}
{Golden Gate Technology, Moscow}
{}
{Software Developer / Senior Software Developer}
{Small-sized technological startup with offices in Moscow and San Jose (USA), developing set of tools
to automate physical design high-performance electronic chips. The focus was to reduce power consumption
for portable and wireless devices. I was a member of Routing team (2 people in Russia, 2 in USA),
specializing in detailed (final) routing. Geometric algorithms that were implemented on C and C++ using parallel computations.}
{\begin{itemize}
\item{Developed routing engine to interconnect components to power and ground meshes.}
\item{Supported various complex design rules for technologies 65nm and below, enhanced and speeded up ripup-and-reroute maze engine.}
\item{Wrote geographical-based database for storing and lookup routing topology.}
\end{itemize}}
{\rule{0mm}{5mm}\textbf{Technologies:} C/C++/STL (gcc), PThreads, Perl, Qt, TCL, RPC XDR.\\
\rule{0mm}{5mm}\textbf{Operating Systems:} RedHat Linux 7 (Server, GUI, IDE).\\
\rule{0mm}{5mm}\textbf{SDLC:} Vim, CVS, Make, GDB/DDD, Valgrind, GProf, OProfile, GCov.
}

%----------------------------------------------------------------------------------------
%	EDUCATION 
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{1997-2002} \> MS, Mathematics - \href{http://en.math.msu.su}
{Moscow State University, Department of Mechanics and Mathematics}\\[5pt]
\>\+
\textit{GPA 4.5/5.0, Red Diploma}\\
\textit{Thesis - "Generalized Assignment Problem"}
}

%------------------------------------------------

\tabbedblock{
\bf{2002-2005} \> PhD, Philosophy - Russian Institute of Culturology\\[5pt]
\>\+
\textit{Thesis - "Science Tradition as Sociocultural Phenomena }\\
\textit{(by the example of Moscow Philosophic and Mathematics School)"}
}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS 
%----------------------------------------------------------------------------------------

\section{Certifications}

\tabbedblock{
\bf{2018} \> \href{https://www.youracclaim.com/badges/d4d28c0e-02c5-455c-8090-e56697741cfc/linked_in_profile}
{Oracle Certified Associate, Java SE 8 Programmer (1Z0-808)}\\[5pt]
\bf{2019} \> \href{https://www.youracclaim.com/badges/52a249a3-1a6b-4343-a724-b41a5afac1e8/linked_in_profilee}
{Oracle Certified Professional, Java SE 8 Programmer (1Z0-809)}\\[5pt]
\bf{2019} \> \href{https://www.coursera.org/account/accomplishments/verify/34HMBYWQ7QLW}
{Coursera, Kotlin for Java Developers}\\[5pt]
\bf{2021} \> \href{https://www.credential.net/70e6e718-60e1-47af-8759-ce102bebb726?key=7f9827277e739814eeb3d3f5bb843a1a3ae15c892191923f2a4469e6cedc9c3b}
{Google Cloud Certified Professional Cloud Architect}\\[5pt]
\>\+
}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Professional Skills}

\skillgroup{Programming Languages and Technologies}
{
\textit{Core Java 8, 11, 17, Kotlin, Spring/Spring Boot} - advanced level (design and code review mostly), 10+ years of experience.\\
\textit{Python2/3, NumPy, SciPy} - advanced level, 5 years of experience.\\
\textit{Messaging middleware: Apache Kafka, Redis, Tibco JMS, Tibco Rendezvous, Informatica LBM, Solace} - good level at design.\\
\textit{Multi-threading, POSIX Threads, CPython Threads} - good level, however was not used daily.\\
\textit{C++03, C++11, STL, Boost} - advanced level, 10+ years of experience, not used for quite a while.\\
\textit{Other scripting languages: Bash, Perl, TCL} -  proficient in Bash, often use Perl one-liners for logs parsing.\\
\textit{TCP, HTTP, WebSockets} - good level on design and code review, not often programmed myself.\\
\textit{Oracle SQL, MySQL} - medium level, normally used schemes were quite simple and small.\\
\textit{ASP.NET, C\#, WPF} - basic knowledge of design and internals, no hands-on experience.
}

%------------------------------------------------

\skillgroup{Operating systems and Platforms}
{
\textit{RedHat Enterprise 7, 8}\\
\textit{Google Anthos, Kubernetes}\\
\textit{SUSE Linux Enterprise 9,11}\\
\textit{Microsoft Windows XP, 7, Server 2016, Server 2019}\\
\textit{Sun (Oracle) Solaris for x86/x64}
}

%------------------------------------------------

\skillgroup{Software Development Lifecycle}
{
\textit{Waterfall, Scrum, Kanban} - development methodologies.\\
\textit{Atlassian Confluence, Jira} - requirements management.\\
\textit{GIT, BitBucket, SVN, CVS, Rational ClearCase} - source code control.\\
\textit{IntelliJ Idea/PyCharm, Eclipse CDT/PyDev, Visual Studio, Vim} - Integrated Development Environments.\\
\textit{Gradle, Maven, CMake, Make} - build machinery.\\
\textit{TeamCity, Jenkins/Hudson, IBM UrbanCode} - continuous integration.\\
\textit{Java Mission Control, GDB, Valgrind, GProf, GCov, OProfile, Coverage} - profiling and performance.\\ 
\textit{JUnit, Nose, Cucumber} - automated testing frameworks.\\
\textit{ITRS Geneos} - real-time monitoring.
}

%------------------------------------------------

\skillgroup{Miscellaneous}
{
\textit{Foreign Languages} - fluent English speaker. All business correspondence in English for 10+ years. Deutsch - B1, reading and writing \\
\textit{Business Writing} - able to cope with big emails flow (500+ emails per day) having Inbox clean. \\
\textit{Project Management} - hands-on experience with Microsoft Project, using sequencing and resource assignment for target date estimation.\\
\textit{Presentation Skills} - 5-10 presentations per year to Senior IT and business stakeholders during last 10 years.
}

%----------------------------------------------------------------------------------------
%	PERSONAL SECTION
%----------------------------------------------------------------------------------------

\section{Personal Details}

\personalgroup{
\personal{Married. Three children: son (14 years) and daughters (12 and 7 years).}
\personal{I like business trips because they are very important for establishing relations between distant teams.}
\personal{Relocated in 2022 from Moscow, Russia to Berlin, Germany. Open to further relocations.}
\personal{I love running and listening music (electronic helps me to focus at work).}
\personal{Prefer historical literature, philosophy, sociology and auteur cinema.}
}

\begin{comment}
%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

\section{Referees}

\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Bill Lumbergh \\ % Referee name
{\bf Company} \> Initech Inc. \\ % Referee company
{\bf Position} \> Vice President \\ % Referee job title 
{\bf Contact} \> \href{mailto:bill@initech.com}{bill@initech.com} % Referee contact information
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Michael "Big Mike" Tucker\\ % Referee name
{\bf Company} \> Burbank Buy More \\ % Referee company
{\bf Position} \> Store Manager \\ % Referee job title 
{\bf Contact} \> \href{mailto:mike@buymore.com}{mike@buymore.com} % Referee contact information
\end{tabbing}}

%----------------------------------------------------------------------------------------
\end{comment}

\end{document}
